---
title: "SNA_reciprocity"
author: "Yingyue Jiang"
date: "2025-04-19"
output: pdf_document
---
This code is for the analysis of the line charts of the number of visa-free countries a passport-hold can enter and the number of countries a country that allows citizens from other countries can enter. I will first try to plot the line chart for 17 selected countries and then for different continents and developed and developing countries

As I want to see the difference before and after 2019, so I add years before around 2010, and as there might be some countries not in the previous year, I might need to select some countries 

```{r}
rm(list = ls())
knitr::opts_chunk$set(message = F)
knitr::opts_chunk$set(warning = F)
knitr::opts_chunk$set(fig.height = 4)
knitr::opts_chunk$set(fig.width = 6)
knitr::opts_chunk$set(fig.align="center")
`%notin%` <- Negate(`%in%`)
library(kableExtra)
library(haven)
library(purrr)
library(dplyr)
library(igraph)
library(ggplot2)
library(sna) #data visualiztion, cleaning, network analysis
library(tidyr)
library(network)
library(readxl)
```

# import data

```{r}
setwd("/Users/yingyuejiang/Desktop/Brown University/SOC 2960/visa policy/visa_data/visa")
#visa_202312_new<-read.csv("202501.csv")
```


```{r}
setwd("/Users/yingyuejiang/Desktop/Brown University/SOC 2960/visa policy/visa_data/visa")
#self constructed
visa_201301<-read.csv("201301.csv")
visa_201201<-read.csv("201201.csv")
visa_201101<-read.csv("201101.csv")
visa_201001<-read.csv("201001.csv")
visa_200901<-read.csv("200901.csv")
visa_200801<-read.csv("200801.csv")
visa_200701<-read.csv("200701.csv")
visa_200601<-read.csv("200601.csv")
visa_200501<-read.csv("200501.csv")
#already collected
visa_202002<-read.csv("202002.csv")
visa_202003<-read.csv("202003.csv")
visa_202004<-read.csv("202004.csv")
visa_202005<-read.csv("202005.csv")
visa_202011<-read.csv("202011.csv")
visa_202101<-read.csv("202101.csv")
visa_202102<-read.csv("202102.csv")
visa_202105<-read.csv("202105.csv")
visa_202108<-read.csv("202108.csv")
visa_202109<-read.csv("202109.csv")
visa_202110<-read.csv("202110.csv")
visa_202111<-read.csv("202111.csv")
visa_202112<-read.csv("202112.csv")
visa_202201<-read.csv("202201.csv")
visa_202202<-read.csv("202202.csv")
visa_202203<-read.csv("202203.csv")
visa_202204<-read.csv("202204.csv")
visa_202205<-read.csv("202205.csv")
visa_202206<-read.csv("202206.csv")
visa_202207<-read.csv("202207.csv")
visa_202208<-read.csv("202208.csv")
visa_202209<-read.csv("202209.csv")
visa_202210<-read.csv("202210.csv")
visa_202211<-read.csv("202211.csv")
visa_202212<-read.csv("202212.csv")
visa_202301<-read.csv("202301.csv")
visa_202302<-read.csv("202302.csv")
visa_202304<-read.csv("202304.csv")
visa_202305<-read.csv("202305.csv")
visa_202306<-read.csv("202306.csv")
visa_202307<-read.csv("202307.csv")
visa_202308<-read.csv("202308.csv")
visa_202309<-read.csv("202309.csv")
visa_202310<-read.csv("202310.csv")
visa_202311<-read.csv("202311.csv")
visa_202312<-read.csv("202312.csv")
visa_202401<-read.csv("202401.csv")
visa_202402<-read.csv("202402.csv")
visa_202403<-read.csv("202403.csv")
visa_202404<-read.csv("202404.csv")
visa_202405<-read.csv("202405.csv")
visa_202406<-read.csv("202406.csv")
visa_202407<-read.csv("202407.csv")
visa_202408<-read.csv("202408.csv")
visa_202410<-read.csv("202410.csv")
visa_202411<-read.csv("202411.csv")
visa_202412<-read.csv("202412.csv")
visa_202501<-read.csv("202501.csv")

```


```{r}
#need to select only 184 countries
# Vector of all dataset names
visa_201301<-visa_201301%>%
  mutate(across(-Passport, ~ ifelse(. %in% (1), 1, "no")))
visa_201201<-visa_201201%>%
  mutate(across(-Passport, ~ ifelse(. %in% (1), 1, "no")))
visa_201101<-visa_201101%>%
  mutate(across(-Passport, ~ ifelse(. %in% (1), 1, "no")))
visa_201001<-visa_201001%>%
  mutate(across(-Passport, ~ ifelse(. %in% (1), 1, "no")))
visa_200901<-visa_200901%>%
  mutate(across(-Passport, ~ ifelse(. %in% (1), 1, "no")))
visa_200801<-visa_200801%>%
  mutate(across(-Passport, ~ ifelse(. %in% (1), 1, "no")))
visa_200701<-visa_200701%>%
  mutate(across(-Passport, ~ ifelse(. %in% (1), 1, "no")))
visa_200601<-visa_200601%>%
  mutate(across(-Passport, ~ ifelse(. %in% (1), 1, "no")))
visa_200501<-visa_200501%>%
  mutate(across(-Passport, ~ ifelse(. %in% (1), 1, "no")))

visa_datasets <- c(
  "visa_202002", "visa_202003", "visa_202004", "visa_202005", "visa_202011",
  "visa_202101", "visa_202102", "visa_202105", "visa_202108", "visa_202109",
  "visa_202110", "visa_202111", "visa_202112", "visa_202201", "visa_202202",
  "visa_202203", "visa_202204", "visa_202205", "visa_202206", "visa_202207",
  "visa_202208", "visa_202209", "visa_202210", "visa_202211", "visa_202212",
  "visa_202301", "visa_202302", "visa_202304", "visa_202305", "visa_202306",
  "visa_202307", "visa_202308", "visa_202309", "visa_202310", "visa_202311",
  "visa_202312", "visa_202401", "visa_202402", "visa_202403", "visa_202404",
  "visa_202405", "visa_202406", "visa_202407", "visa_202408", "visa_202410",
  "visa_202411", "visa_202412", "visa_202501"
)

# Filter all datasets to only include rows with Passport in visa_201301$passport
for (dataset in visa_datasets) {
  df <- get(dataset)
  df <- df %>% filter(Passport %in% visa_201301$Passport)
  # Replace "." with " " in column names
  colnames(df) <- gsub("\\.", " ", colnames(df))

  # Convert Passport to character to avoid factor-related if_else issues

  # Standardize Passport values
  df$Passport[df$Passport == "Guinea-Bissau"] <- "Guinea Bissau"
  df$Passport[df$Passport == "Timor-Leste"] <- "Timor Leste"
 
  # Now filter columns to keep only "Passport" and those that match values in Passport column
  row_names <- df$Passport
  cols_to_keep <- intersect(colnames(df), row_names)
  df <- df %>% select(Passport, all_of(cols_to_keep))

  # Save back the modified dataset
  assign(dataset, df)
}
```



```{r}
# Define visa-free values
visa_free_values <- c("90", "30", "180", "28", "21", "360", "60", "240", "14",
                      "120", "42", "15", "45", "150", "10", "7", 
                      "VOA", "VF", "visa on arrival", "visa free", "31","1")


# Grab all objects in the environment that start with "visa_"
visa_names <- ls(pattern = "^visa_\\d{6}$")
visa_list <- mget(visa_names)

library(dplyr)

visa_list <- lapply(visa_list, function(df) {
  df %>% mutate(across(everything(), ~ ifelse(. %in% visa_free_values, "visa free", .)))
})

list2env(visa_list, envir = .GlobalEnv)
```

#plot 17 countries 

```{r}
target_passports <- c("Afghanistan", "Brazil", "China", "Germany", "Iran",
                      "Japan", "Kenya", "Russia", "Somalia", "South Africa",
                      "South Korea", "United States")
# Grab all visa datasets you want to filter
visa_names <- ls(pattern = "^visa_\\d{6}$")
visa_list <- mget(visa_names)
# Filter each dataset and store with new names
selected_list <- lapply(visa_list, function(df) {
  df %>% filter(Passport %in% target_passports)
})

# Rename each selected dataframe
names(selected_list) <- paste0("selected_", gsub("visa_", "", names(visa_list)))

# Save each one back to the global environment
list2env(selected_list, envir = .GlobalEnv)

```


```{r}
selected_names <- ls(pattern = "^selected_\\d{6}$")

# Step 2: Bind all with YearMonth column added
selected_all <- selected_names %>%
  map_dfr(~ {
    df <- get(.x)
    df[] <- lapply(df, as.character)
    ym <- gsub("selected_", "", .x)
    df %>% mutate(YearMonth = as.Date(paste0(substr(ym, 1, 4), "-", substr(ym, 5, 6), "-01")),
                  VF_count = rowSums(. == "visa free"))
  })
```

```{r}
selected_all %>%
  filter(Passport %in% c("Afghanistan", "United States")) %>%
  select(Passport, VF_count, YearMonth)
```



```{r}
selected_all%>%filter(Passport%in%c("Afghanistan","United States"))%>%select(VF_count,YearMonth)
```



## plot countries that have access to 

```{r}
library(ggplot2)
library(scales)

# Ensure YearMonth is in Date format
selected_all$YearMonth <- as.Date(paste0(selected_all$YearMonth, "-01"))

# Define yearly x-axis breaks
date_seq <- seq.Date(from = as.Date("2005-01-01"), to = as.Date("2025-01-01"), by = "12 month")
selected_all <- selected_all %>%
  arrange(Passport, YearMonth)
# Plot
ggplot(selected_all, aes(x = YearMonth, y = VF_count, color = Passport, group = Passport)) +
  geom_line(size = 1) +
  geom_point(size = 1) +
  labs(
    title = "Number of visa-free countries for passport holders",
    subtitle = "2005-2025",
    x = "Year",
    y = "Number of Visa-Free Countries",
    color = "Passport"
  ) +
  scale_x_date(labels = date_format("%Y-%m"), breaks = date_seq) +
  scale_y_continuous(limits = c(0, 180), breaks = seq(0, 200, by = 20)) +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 11) +
  theme(
    axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA),
    legend.background = element_rect(fill = "white", color = NA)
  )

ggsave("visa_0525.jpg", width = 10, height = 6, dpi = 300) 
```




## plot countries that they grant visa-free access to 

```{r}
# Get all visa_* dataset names
visa_names <- ls(pattern = "^visa_\\d{6}$")

# Loop through and update names in-place
for (name in visa_names) {
  df <- get(name)
  names(df) <- gsub("\\.", " ", names(df))  # Replace dots with spaces
  assign(name, df)  # Save it back to the same name
}

```


```{r}
library(dplyr)
library(purrr)
library(tibble)

# Get all visa_* dataset names
visa_names <- ls(pattern = "^visa_\\d{6}$")
target_passports <- c("Afghanistan", "Brazil", "China", "Germany", "Iran",
                      "Japan", "Kenya", "Russia", "Somalia", "South Africa",
                      "South Korea", "United States")

# Process each: select columns, transpose, convert to data frame, and add YearMonth
transposed_all <- visa_names %>%
  map_dfr(~ {
    df <- get(.x)
    ym <- gsub("visa_", "", .x)
    year_month <- as.Date(paste0(substr(ym, 1, 4), "-", substr(ym, 5, 6), "-01"))
    
    # Keep only columns that are present
    existing_countries <- intersect(target_passports, colnames(df))
    df_selected <- df %>% select(all_of(existing_countries))

    # Transpose and reformat
    df_transposed <- as.data.frame(t(df_selected)) %>%
      rownames_to_column(var = "Country") %>%
      mutate(YearMonth = year_month)
    
    return(df_transposed)
  })

```

```{r}
transposed_all%>%filter()
```

```{r}
View(transposed_all)
```



```{r}
transposed_all <- transposed_all %>%
  mutate(VF_count= rowSums(select(., where(is.character)) == "visa free", na.rm = TRUE))

# Ensure YearMonth is in Date format
transposed_all$YearMonth <- as.Date(paste(transposed_all$YearMonth, "01", sep = "-"), format = "%Y-%m-%d")
date_seq <- seq.Date(from = as.Date("2005-01-01"), to = as.Date("2025-01-01"), by = "12 month")
# Plotting a line plot for VF_count over time by Passport
ggplot(transposed_all, aes(x = YearMonth, y = VF_count, color = Country, group = Country)) +
  geom_line(size = 1) +  # Line plot for each passport
  geom_point(size = 1) +  # Adding points for clarity
  labs(title = "Number of countries to which the selected country grants visa-free access",
       subtitle="2005-2025",
       x = "Year-Month",
       y = "Number of Countries",
       color = "Receiving country") +
  theme_minimal() +
  scale_x_date(labels = date_format("%Y-%m"),breaks = date_seq) +  # Formatting x-axis as date
  scale_y_continuous(limits = c(0,200),breaks=seq(0, 200, by = 20))+
   scale_color_brewer(palette = "Paired")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+# Rotate x-axis labels for readability 
  theme(
    axis.text.x = element_text(size = 8, angle = 45, hjust = 1),  # Reduce font size of x-axis
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA),
    legend.background = element_rect(fill = "white", color = NA), 
    panel.grid = element_blank() #remove grid
  )
ggsave("grant_0525.jpg", width = 10, height = 6, dpi = 300) 
```



#plot continents

```{r}
setwd("/Users/yingyuejiang/Desktop/Brown University/SOC 2960/visa policy/visa_data/visa")
library(readxl)
country_list<-read_excel("country_list.xlsx")
```


```{r}
#change country name
visa_201301<-visa_201301%>%mutate(Passport=if_else(Passport%in%c("Guinea-Bissau"),"Guinea Bissau",Passport),
                                  Passport=if_else(Passport%in%c("Timor-Leste"),"Timor Leste",Passport))
visa_201201<-visa_201201%>%mutate(Passport=if_else(Passport%in%c("Guinea-Bissau"),"Guinea Bissau",Passport),
                                  Passport=if_else(Passport%in%c("Timor-Leste"),"Timor Leste",Passport))
visa_201101<-visa_201101%>%mutate(Passport=if_else(Passport%in%c("Guinea-Bissau"),"Guinea Bissau",Passport),
                                  Passport=if_else(Passport%in%c("Timor-Leste"),"Timor Leste",Passport))
visa_201001<-visa_201001%>%mutate(Passport=if_else(Passport%in%c("Guinea-Bissau"),"Guinea Bissau",Passport),
                                  Passport=if_else(Passport%in%c("Timor-Leste"),"Timor Leste",Passport))
visa_200901<-visa_200901%>%mutate(Passport=if_else(Passport%in%c("Guinea-Bissau"),"Guinea Bissau",Passport),
                                  Passport=if_else(Passport%in%c("Timor-Leste"),"Timor Leste",Passport))
visa_200801<-visa_200801%>%mutate(Passport=if_else(Passport%in%c("Guinea-Bissau"),"Guinea Bissau",Passport),
                                  Passport=if_else(Passport%in%c("Timor-Leste"),"Timor Leste",Passport))
visa_200701<-visa_200701%>%mutate(Passport=if_else(Passport%in%c("Guinea-Bissau"),"Guinea Bissau",Passport),
                                  Passport=if_else(Passport%in%c("Timor-Leste"),"Timor Leste",Passport))
visa_200601<-visa_200601%>%mutate(Passport=if_else(Passport%in%c("Guinea-Bissau"),"Guinea Bissau",Passport),
                                  Passport=if_else(Passport%in%c("Timor-Leste"),"Timor Leste",Passport))
visa_200501<-visa_200501%>%mutate(Passport=if_else(Passport%in%c("Guinea-Bissau"),"Guinea Bissau",Passport),
                                  Passport=if_else(Passport%in%c("Timor-Leste"),"Timor Leste",Passport))
```


```{r}
country_common<-country_list%>%filter(Passport%in%visa_201301$Passport)
```



```{r}

process_visa_table <- function(df_name) {
  # Retrieve the data frame from the global environment
  df <- get(df_name, envir = .GlobalEnv)

  # Extract time value from table name (e.g., "visa_202501" -> 202501)
  time_value <- as.numeric(gsub("\\D", "", df_name))

  # Count occurrences of "visa free" in each row (excluding the 'passport' column)
  df$visa_free_count <- rowSums(df == "visa free", na.rm = TRUE)

  # Add time column
  df$time <- time_value
  df$developed <-country_common$Developed
  df$continent <-country_common$Continent

  # Select relevant columns
  df_processed <- df %>%
    select(Passport, visa_free_count, time,developed,continent)

  return(df_processed)
}

```



```{r}
library(dplyr)

process_visa_table_before <- function(df_name) {
  # Retrieve the data frame from the global environment
  df <- get(df_name, envir = .GlobalEnv)

  # Extract time value from table name (e.g., "visa_202501" -> 202501)
  time_value <- as.numeric(gsub("\\D", "", df_name))

  # Count occurrences of "visa free" in each row (excluding the 'Passport' column)
  df$visa_free_count <- rowSums(df[, -1] == "visa free", na.rm = TRUE)

  # Add time column
  df$time <- time_value

  # Merge with country_common by Passport
  df_merged <- df %>%
    left_join(country_common, by = "Passport")

  # Select relevant columns
  df_processed <- df_merged %>%
    select(Passport, visa_free_count, time, Developed, Continent) %>%
    rename(developed = Developed, continent = Continent)

  return(df_processed)
}

```



```{r}
#before 2005
new_201301<-process_visa_table_before("visa_201301")
new_201201<-process_visa_table_before("visa_201201")
new_201101<-process_visa_table_before("visa_201101")
new_201001<-process_visa_table_before("visa_201001")
new_200901<-process_visa_table_before("visa_200901")
new_200801<-process_visa_table_before("visa_200801")
new_200701<-process_visa_table_before("visa_200701")
new_200601<-process_visa_table_before("visa_200601")
new_200501<-process_visa_table_before("visa_200501")
```


```{r}

#2020
new_202002<-process_visa_table("visa_202002")
new_202003<-process_visa_table("visa_202003")
new_202004<-process_visa_table("visa_202004")
new_202005<-process_visa_table("visa_202005")
new_202011<-process_visa_table("visa_202011")
#2021
new_202102<-process_visa_table("visa_202102")
new_202105<-process_visa_table("visa_202105")
new_202108<-process_visa_table("visa_202108")
new_202109<-process_visa_table("visa_202109")
new_202110<-process_visa_table("visa_202110")
new_202111<-process_visa_table("visa_202111")
new_202112<-process_visa_table("visa_202112")
#2022
new_202201<-process_visa_table("visa_202201")
new_202202<-process_visa_table("visa_202202")
new_202203<-process_visa_table("visa_202203")
new_202204<-process_visa_table("visa_202204")
new_202205<-process_visa_table("visa_202205")
new_202206<-process_visa_table("visa_202206")
new_202207<-process_visa_table("visa_202207")
new_202208<-process_visa_table("visa_202208")
new_202209<-process_visa_table("visa_202209")
new_202210<-process_visa_table("visa_202210")
new_202211<-process_visa_table("visa_202211")
new_202212<-process_visa_table("visa_202212")
#2023
new_202301<-process_visa_table("visa_202301")
new_202302<-process_visa_table("visa_202302")
new_202304<-process_visa_table("visa_202304")
new_202305<-process_visa_table("visa_202305")
new_202306<-process_visa_table("visa_202306")
new_202307<-process_visa_table("visa_202307")
new_202308<-process_visa_table("visa_202308")
new_202309<-process_visa_table("visa_202309")
new_202310<-process_visa_table("visa_202310")
new_202311<-process_visa_table("visa_202311")
new_202312<-process_visa_table("visa_202312")
#2024
new_202401<-process_visa_table("visa_202401")
new_202402<-process_visa_table("visa_202402")
new_202403<-process_visa_table("visa_202403")
new_202404<-process_visa_table("visa_202404")
new_202405<-process_visa_table("visa_202405")
new_202406<-process_visa_table("visa_202406")
new_202407<-process_visa_table("visa_202407")
new_202408<-process_visa_table("visa_202408")
new_202410<-process_visa_table("visa_202410")
new_202411<-process_visa_table("visa_202411")
new_202412<-process_visa_table("visa_202412")
#2025
new1_202501<-process_visa_table("visa_202501")
```

#developed

```{r}
total<-rbind(new_200501,new_200601,new_200701,new_200801,new_200901,new_201001,new_201101,new_201201,new_201301,new_202002,new_202003,new_202004,new_202005,new_202011,new_202102,new_202105,new_202108,new_202109,new_202110,new_202111,new_202112,new_202201,new_202202,new_202203,new_202204,new_202205,new_202206,new_202207,new_202208,new_202209,new_202210,new_202211,new_202212,new_202301,new_202302,new_202304,new_202305,new_202306,new_202307,new_202308,new_202309,new_202310,new_202311,new_202312,new_202401,new_202402,new_202403,new_202404,new_202405,new_202406,new_202407,new_202408,new_202410,new_202411,new_202412,new1_202501)
```

```{r}
library(dplyr)
library(lubridate)
total_new<-total%>%
  mutate(
    time_date = as.Date(paste0(time, "01"), format = "%Y%m%d"),  # Convert to Date
    time_diff = as.numeric(interval(as.Date("2020-02-01"), time_date) / months(1)+1) # Compute month difference
  )
```


```{r}
group<-total_new%>%group_by(continent,time_date)%>%
 summarise(
   mean_visa_free=mean(visa_free_count)
 )
global_avg <- total_new %>%
  group_by(time_date) %>%
  summarise(overall_mean = mean(visa_free_count, na.rm = TRUE), .groups = "drop")
group_developed<-total_new%>%group_by(developed,time_date)%>%
 summarise(
   mean_visa_free=mean(visa_free_count)
 )
```

```{r}
unique(group$continent)
```



```{r}
ggplot() +
  geom_line(data = group, aes(x = time_date, y = mean_visa_free, color = continent, group = continent)) +
  geom_point(data = group, aes(x = time_date, y = mean_visa_free, color = continent)) +
  geom_line(data = global_avg, aes(x = time_date, y = overall_mean), color = "black", size = 1, linetype = "dashed") +
  scale_color_brewer(palette = "Set1")+
  labs(
    title = "Mean number of visa-free countries for passport holders by continents",
    subtitle = "Dashed black line shows overall average across all continents at each time point",
    x = "",
    y = "Mean number visa-free countries",
    color = "Continent"
  ) +
  scale_x_date(date_labels = "%Y-%m", date_breaks = "12 months") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#ggsave("change_continent.jpg",width = 10, height = 6, dpi = 300)
```




#plot continents and developed together
```{r}
ggplot() +
  # Continent lines
  geom_line(data = group, aes(x = time_date, y = mean_visa_free, color = continent, group = continent), size = 1) +
  geom_point(data = group, aes(x = time_date, y = mean_visa_free, color = continent)) +

  # Developed status lines (manual color, thicker, semi-transparent)
  geom_line(data = group_developed, aes(x = time_date, y = mean_visa_free, linetype = factor(developed)), color = "grey20", size = 1.2, alpha = 0.5) +

  # Global average line
  geom_line(data = global_avg, aes(x = time_date, y = overall_mean), color = "black", size = 1, linetype = "dashed") +

  # Styling
  scale_color_brewer(palette = "Set1") +
  scale_linetype_manual(
    values = c("0" = "dotdash", "1" = "solid"),
    labels = c("Developing", "Developed")
  ) +
  labs(
    title = "Mean number of visa-free countries for passport holders by continents",
    #subtitle = "dashed black line = global average; grey lines = developed vs developing",
    x = "",
    y = "Mean number of visa-free countries",
    color = "Continent",
    linetype = "Development status",
     caption = "Dashed black line = global average; grey lines = developed vs developing",
  ) +
  scale_x_date(
  date_labels = "%Y-%m",
  breaks = seq(as.Date("2005-01-01"), as.Date("2025-01-01"), by = "1 year"),
  limits = c(as.Date("2005-01-01"), as.Date("2025-01-01"))
)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("change_all1.jpg",width = 10, height = 6, dpi = 300)
```

```{r}
# Filter datasets to only include dates from 2020-02-01 onwards
group_filtered <- subset(group, time_date >= as.Date("2020-02-01"))
group_developed_filtered <- subset(group_developed, time_date >= as.Date("2020-02-01"))
global_avg_filtered <- subset(global_avg, time_date >= as.Date("2020-02-01"))

ggplot() +
  # Continent lines
  geom_line(data = group_filtered, aes(x = time_date, y = mean_visa_free, color = continent, group = continent), size = 1) +
  geom_point(data = group_filtered, aes(x = time_date, y = mean_visa_free, color = continent)) +

  # Developed status lines
  geom_line(data = group_developed_filtered, aes(x = time_date, y = mean_visa_free, linetype = factor(developed)), color = "grey20", size = 1.2, alpha = 0.5) +

  # Global average line
  geom_line(data = global_avg_filtered, aes(x = time_date, y = overall_mean), color = "black", size = 1, linetype = "dashed") +

  # Styling
  scale_color_brewer(palette = "Set1") +
  scale_linetype_manual(
    values = c("0" = "dotdash", "1" = "solid"),
    labels = c("Developing", "Developed")
  ) +
  labs(
    title = "Mean number of visa-free countries for passport holders by continents",
    x = "",
    y = "Mean number of visa-free countries",
    color = "Continent",
    linetype = "Development status",
    caption = "Dashed black line = global average; grey lines = developed vs developing"
  ) +
  scale_x_date(
    date_labels = "%Y-%m",
    breaks = seq(as.Date("2020-02-01"), as.Date("2025-01-01"), by = "1 year"),
    limits = c(as.Date("2020-02-01"), as.Date("2025-01-01"))
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("change_part1.jpg", width = 10, height = 6, dpi = 300)

```



#receiving country




```{r}
column_trans<- function(df_name) {
  df <- get(df_name)
  ym <- gsub("visa_", "", df_name)
  date <- as.Date(paste0(substr(ym, 1, 4), "-", substr(ym, 5, 6), "-01"))

  counts <- colSums(df == "visa free", na.rm = TRUE)
  tibble(
    Passport = names(counts),
    visa_free_count = as.integer(counts),
    YearMonth = date
  ) %>%
    left_join(country_common, by = c("Passport" = "Country")) %>%
    rename(continent = Continent, developed = Developed)
}

```


```{r}
library(dplyr)
library(purrr)
library(tibble)

column_trans<- function(df_name) {
  df <- get(df_name)
  ym <- gsub("visa_", "", df_name)
  date <- as.Date(paste0(substr(ym, 1, 4), "-", substr(ym, 5, 6), "-01"))
  
  # Count "visa free" per Passport column
  counts <- colSums(df == "visa free", na.rm = TRUE)
  
  # Build a tibble with Passport, counts, and YearMonth
  tibble(
    Passport       = names(counts),
    visa_free_count = as.integer(counts),
    YearMonth      = date
  ) %>%
    # Now join by Passport (same name in both df and country_list)
    left_join(country_common, by = "Passport") %>%
    # Rename the joined columns
    rename(
      continent = Continent,
      developed = Developed
    )
}

# List all your visa_YYYYMM data frames
visa_table_names <- ls(pattern = "^visa_\\d{6}$")

# Apply and row-bind them all
all_processed <- map_dfr(visa_table_names, column_trans)

```



```{r}
all_processed_new<-all_processed%>%filter(Passport!="Passport")%>%drop_na(continent)
```

```{r}
receive_group<-all_processed_new%>%group_by(continent,YearMonth)%>%
 summarise(
   mean_visa_free=mean(visa_free_count)
 )
```


```{r}

receive_avg <-all_processed_new %>%
  group_by(YearMonth) %>%
  summarise(overall_mean = mean(visa_free_count, na.rm = TRUE), .groups = "drop")
receive_develop<-all_processed_new%>%drop_na(continent)%>%group_by(developed,YearMonth)%>%
 summarise(
   mean_visa_free=mean(visa_free_count)
 )
```


```{r}
ggplot() +
  # Continent lines
  geom_line(data = receive_group, aes(x = YearMonth, y = mean_visa_free, color = continent, group = continent), size = 1) +
  geom_point(data = receive_group, aes(x = YearMonth, y = mean_visa_free, color = continent)) +

  # Developed status lines (manual color, thicker, semi-transparent)
  geom_line(data = receive_develop, aes(x = YearMonth, y = mean_visa_free, linetype = factor(developed)), color = "grey20", size = 1.2, alpha = 0.5) +

  # Global average line
  geom_line(data = receive_avg, aes(x = YearMonth, y = overall_mean), color = "black", size = 1, linetype = "dashed") +

  # Styling
  scale_color_brewer(palette = "Set1") +
  scale_linetype_manual(
    values = c("0" = "dotdash", "1" = "solid"),
    labels = c("Developing", "Developed")
  ) +
  labs(
    title = "Mean number of countries to which the selected country grant visa-free access by continents",
    #subtitle = "dashed black line = global average; grey lines = developed vs developing",
    x = "",
    y = "Mean number of countries",
    color = "Continent",
    linetype = "Development status",
     caption = "Dashed black line = global average; grey lines = developed vs developing",
  ) +
  scale_x_date(
  date_labels = "%Y-%m",
  breaks = seq(as.Date("2005-01-01"), as.Date("2025-01-01"), by = "1 year"),
  limits = c(as.Date("2005-01-01"), as.Date("2025-01-01"))
)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#ggsave("receive_all.jpg",width = 10, height = 6, dpi = 300)
```

```{r}
# Filter data
receive_group_filtered <- subset(receive_group, YearMonth >= as.Date("2020-02-01"))
receive_develop_filtered <- subset(receive_develop, YearMonth >= as.Date("2020-02-01"))
receive_avg_filtered <- subset(receive_avg, YearMonth >= as.Date("2020-02-01"))

# Plot
ggplot() +
  # Continent lines
  geom_line(data = receive_group_filtered, aes(x = YearMonth, y = mean_visa_free, color = continent, group = continent), size = 1) +
  geom_point(data = receive_group_filtered, aes(x = YearMonth, y = mean_visa_free, color = continent)) +

  # Developed status lines
  geom_line(data = receive_develop_filtered, aes(x = YearMonth, y = mean_visa_free, linetype = factor(developed)), color = "grey20", size = 1.2, alpha = 0.5) +

  # Global average line
  geom_line(data = receive_avg_filtered, aes(x = YearMonth, y = overall_mean), color = "black", size = 1, linetype = "dashed") +

  # Styling
  scale_color_brewer(palette = "Set1") +
  scale_linetype_manual(
    values = c("0" = "dotdash", "1" = "solid"),
    labels = c("Developing", "Developed")
  ) +
  labs(
    title = "Mean number of countries to which the selected country grants visa-free access by continent",
    x = "",
    y = "Mean number of countries",
    color = "Continent",
    linetype = "Development status",
    caption = "Dashed black line = global average; grey lines = developed vs developing"
  ) +
  scale_x_date(date_labels = "%b %Y", date_breaks = "12 months") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("receive_part.jpg",width = 10, height = 6, dpi = 300)
```



#reciprocity
```{r}
recip_table<- function(df) {
  # Extract time from the object name
  df_name <- deparse(substitute(df))
  time <- substr(df_name, nchar(df_name) - 5, nchar(df_name))
  
  # Step 0: Clean column names
  colnames(df) <- gsub("\\.", " ", colnames(df))
  
  # Step 0.5: Clean Passport names
  df <- df %>%
    mutate(
      Passport = if_else(Passport == "Guinea-Bissau", "Guinea Bissau", Passport),
      Passport = if_else(Passport == "Timor-Leste", "Timor Leste", Passport)
    )
  
  # Step 1: Reorder columns to match Passport column
  passport_order <- as.character(df$Passport)
  passport_order <- passport_order[passport_order %in% colnames(df)]
  all_columns <- c("Passport", passport_order)
  all_columns <- all_columns[all_columns %in% colnames(df)]
  df <- df[, all_columns]
  
  # Step 2: Convert visa types to binary
  df <- df %>%
    mutate(across(everything(), as.character)) %>%
    mutate(across(everything(), ~ ifelse(. %in% c("visa free", "visa on arrival"), 1, .))) %>%
    mutate(across(everything(), ~ ifelse(. %in% c("no admission", "-1", "e-visa", "eta", "visa required", "VR", "ETA","covid ban","EVW","Hayya Entry Permit","no"), 0, .)))
  
  # Step 3: Set row names and drop Passport column
  rownames(df) <- df$Passport
  df$Passport <- NULL
  
  # Step 4: Convert to numeric matrix
  matrix_result <- as.matrix(df)
  matrix_result <- apply(matrix_result, c(1, 2), as.numeric)
  
  # Step 5: Create igraph object
  graph <- graph_from_adjacency_matrix(adjmatrix = matrix_result, mode = "directed")
  
  # Step 6: Calculate metrics
  reciprocity_score <- igraph::reciprocity(graph) #Arc-based reciprocity
  dyad_recip<-igraph::reciprocity(graph,mode="ratio")
  density <- igraph::edge_density(graph)
  
  # Step 7: Return result as a data frame
  return(data.frame(
    time = time,
    reciprocity_score = reciprocity_score,
    density = density,
    dyad_recip= dyad_recip
  ))
}
```



```{r}
visa_200501_new1<-recip_table(visa_200501)
visa_200601_new1<-recip_table(visa_200601)
visa_200701_new1<-recip_table(visa_200701)
visa_200801_new1<-recip_table(visa_200801)
visa_200901_new1<-recip_table(visa_200901)
visa_201001_new1<-recip_table(visa_201001)
visa_201101_new1<-recip_table(visa_201101)
visa_201201_new1<-recip_table(visa_201201)
visa_201301_new1<-recip_table(visa_201301)

```



```{r}
visa_202002_new1<-recip_table(visa_202002)
visa_202003_new1<-recip_table(visa_202003)
visa_202004_new1<-recip_table(visa_202004)
visa_202005_new1<-recip_table(visa_202005)
visa_202011_new1<-recip_table(visa_202011)
visa_202101_new1<-recip_table(visa_202101)
visa_202102_new1<-recip_table(visa_202102)
visa_202105_new1<-recip_table(visa_202105)
visa_202108_new1<-recip_table(visa_202108)
visa_202109_new1<-recip_table(visa_202109)
visa_202110_new1<-recip_table(visa_202110)
visa_202111_new1<-recip_table(visa_202111)
visa_202112_new1<-recip_table(visa_202112)
visa_202201_new1<-recip_table(visa_202201)
visa_202202_new1<-recip_table(visa_202202)
visa_202203_new1<-recip_table(visa_202203)
visa_202204_new1<-recip_table(visa_202204)
visa_202205_new1<-recip_table(visa_202205)
visa_202206_new1<-recip_table(visa_202206)
visa_202207_new1<-recip_table(visa_202207)
visa_202208_new1<-recip_table(visa_202208)
visa_202209_new1<-recip_table(visa_202209)
visa_202211_new1<-recip_table(visa_202211)
visa_202212_new1<-recip_table(visa_202212)
visa_202301_new1<-recip_table(visa_202301)
visa_202304_new1<-recip_table(visa_202304)
visa_202305_new1<-recip_table(visa_202305)
visa_202306_new1<-recip_table(visa_202306)
visa_202307_new1<-recip_table(visa_202307)
visa_202308_new1<-recip_table(visa_202308)
visa_202309_new1<-recip_table(visa_202309)
visa_202310_new1<-recip_table(visa_202310)
visa_202311_new1<-recip_table(visa_202311)
visa_202312_new1<-recip_table(visa_202312)
visa_202401_new1<-recip_table(visa_202401)
visa_202402_new1<-recip_table(visa_202402)
visa_202403_new1<-recip_table(visa_202403)
visa_202404_new1<-recip_table(visa_202404)
visa_202405_new1<-recip_table(visa_202405)
visa_202406_new1<-recip_table(visa_202406)
visa_202407_new1<-recip_table(visa_202407)
visa_202408_new1<-recip_table(visa_202408)
visa_202410_new1<-recip_table(visa_202410)
visa_202411_new1<-recip_table(visa_202411)
visa_202412_new1<-recip_table(visa_202412)
visa_202501_new1<-recip_table(visa_202501)

```

```{r}
visa_200501_new1
```

```{r}
total_recip<-rbind(visa_200501_new1,visa_200601_new1,visa_200701_new1,visa_200801_new1,visa_200901_new1,visa_201001_new1,visa_201101_new1,visa_201201_new1,visa_201301_new1,visa_202002_new1, visa_202003_new1,visa_202004_new1, visa_202005_new1, visa_202011_new1,visa_202101_new1, visa_202102_new1, visa_202105_new1, visa_202108_new1, visa_202109_new1,visa_202110_new1, visa_202111_new1, visa_202112_new1, visa_202201_new1, visa_202202_new1, visa_202203_new1, visa_202204_new1, visa_202205_new1, visa_202206_new1, visa_202207_new1, visa_202208_new1, visa_202209_new1, visa_202211_new1, visa_202212_new1, visa_202301_new1, visa_202304_new1, visa_202305_new1, visa_202306_new1, visa_202307_new1, visa_202308_new1,visa_202309_new1,visa_202310_new1, visa_202311_new1, visa_202312_new1,visa_202401_new1,visa_202402_new1, visa_202403_new1, visa_202404_new1, visa_202405_new1, visa_202406_new1,visa_202407_new1, visa_202408_new1, visa_202410_new1, visa_202411_new1, visa_202412_new1,visa_202501_new1)
```

```{r}
total_recip <- total_recip %>%
  mutate(
    time = as.Date(paste0(as.character(time), "01"), format = "%Y%m%d")
  )
```


```{r}
ggplot(total_recip, aes(x = time)) +
  # Reciprocity score as a line
  geom_line(aes(y = reciprocity_score, color = "Arc-based reciprocity"), size = 1) +
    geom_line(aes(y = dyad_recip, color = "Dyad-based reciprocity"), size = 1) +
  geom_line(aes(y = density, color = "Density"), size = 1.2) +
  # Density score as points
  geom_point(aes(y = density, color = "Density"), size = 2) +
   geom_point(aes(y = reciprocity_score, color = "Arc-based reciprocity"), size = 2) +
   geom_point(aes(y = dyad_recip, color = "Dyad-based reciprocity"), size = 2) +
  # Manual colors & legend title
  scale_color_manual(
    name   = "Measures",
    values = c("Arc-based reciprocity" = "#1f77b4", "Density" = "#ff7f0e","Dyad-based reciprocity"="red")
  ) +
  # Labels and theme
  labs(
    title = "Reciprocity and density scores over time",
    x     = "",
    y     = "Score"
  ) +
  scale_x_date(
  date_labels = "%Y-%m",
  breaks = seq(as.Date("2005-01-01"), as.Date("2025-01-01"), by = "1 year"),
  limits = c(as.Date("2005-01-01"), as.Date("2025-01-01"))
)+
  scale_y_continuous(
    limits = c(0,1),
    breaks=seq(0,1,by=0.2)
  )+
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  )
ggsave("recip_plot_0525.jpg",width = 10, height = 6, dpi = 300)
```

```{r}
library(dplyr)
library(ggplot2)

ggplot(filter(total_recip, time >= as.Date("2020-02-01")), aes(x = time)) +
  geom_line(aes(y = reciprocity_score, color = "Arc-based reciprocity"), size = 1) +
  geom_line(aes(y = dyad_recip, color = "Dyad-based reciprocity"), size = 1) +
  geom_line(aes(y = density, color = "Density"), size = 1.2) +
  geom_point(aes(y = density, color = "Density"), size = 2) +
  geom_point(aes(y = reciprocity_score, color = "Arc-based reciprocity"), size = 2) +
  geom_point(aes(y = dyad_recip, color = "Dyad-based reciprocity"), size = 2) +
  scale_color_manual(
    name = "Measures",
    values = c("Arc-based reciprocity" = "#1f77b4", "Density" = "#ff7f0e", "Dyad-based reciprocity" = "red")
  ) +
  labs(
    title = "Reciprocity and density scores over time",
    x = "",
    y = "Score"
  ) +
  scale_x_date(
    date_labels = "%Y-%m",
    date_breaks = "1 year",
    limits = c(as.Date("2020-02-01"), as.Date("2025-01-01"))
  ) +
  scale_y_continuous(
    limits = c(0, 1),
    breaks = seq(0, 1, by = 0.2)
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  )
ggsave("recip_plot_2025.jpg",width = 10, height = 6, dpi = 300)

```



```{r}
table(country_list$Civilization)%>%prop.table()
```
```{r}
table(new_200501$continent)
```

